The Effects of weather on maize yields: New evidence from Kenya

### 2018-12-17 writing/draft3/draft13.tex
work
the last bits of today ()or yesterday

@@

  \begin{figure}
   \includegraphics{Figure1a_1f.pdf}\label{MarEff1}
\caption{Predicted multiplicative marginal effects of seasonal precipitation (left column) and average seasonal temperature (right column) on maize yields. The first row (a, b) represents the model for all counties, the second row (c, d) is based on the subsample of arid and semi-arid counties (ASAL) and the third row (e, f) represents the model for the non-ASAL counties. Precipitation and temperature (x-axis) are in multiples of their standard deviations. The effects are multiplicative as the models are in log-linear form.}
\end{figure}

>>>>

\textcolor{blue}{we checked this approach by drop1 =anova testing and it turns out that our model is better than each model without one of the variables..Also the automatic step procedure, which we run for comparison gave us almost the same model (forcing the seasonal precip and average temperature). The only varibale which was extra was MaxT and we decided to remove it because of high VIF - or correlation with average temp...Also mention add1}

@@

  \begin{figure}% new plots checked and good 17.dec.2018
   \includegraphics{Figure1a_1f.pdf}\label{MarEff1}
\caption{Predicted multiplicative marginal effects of seasonal precipitation (left column) and average seasonal temperature (right column) on maize yields. The first row (a, b) represents the model for all counties, the second row (c, d) is based on the subsample of arid and semi-arid counties (ASAL) and the third row (e, f) represents the model for the non-ASAL counties. Precipitation and temperature (x-axis) are in multiples of their standard deviations. The effects are multiplicative as the models are in log-linear form.}
\end{figure}
